Ubercalibration Simulations \\(Euclid)

### 2011-01-26 Documentation/ubercal.tex
euclid: documentation update
git-svn-id: svn+ssh://astrometry.net/svn/trunk/projects/euclid@17297 03a3cea6-2c03-0410-ac9b-9271b1c66c29

\subsection{Star Flux Refinement: \textbf{\textit{s\_step}}}
@j, for each star

\begin{equation}
\chi^2 = \sum_{i touching k} \frac{(c_i-f_{ij}s_{kj})^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\frac{d\chi^2}{d s_{kj}} = \sum_{i touching k} \frac{-2 f_{ij} (c_i-f_{ij}s_{kj+1})}{{\sigma_i}^2} = 0
\end{equation}

\begin{equation}
\Rightarrow \sum_{i touching k} \frac{f_{ij} c_i}{{\sigma_i}^2}= \sum_{i touching k} \frac{f_{ij}^2 s_{kj+1}}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\Rightarrow s_{kj+1} = \frac{\sum_{i touching k} \frac{f_{ij} c_i}{{\sigma_i}^2}}/{\sum_{i touching k} \frac{f_{ij}^2 s_{kj+1}}{{\sigma_i}^2}}
\end{equation}

The 
The measurements of each star are refined based on

On the $j$th iteration, the following proce

\subsection{Flat-Field Refinement: \textbf{\textit{p\_step}}}

>>>>

\subsection{Star Flux Refinement: \textbf{\textit{s\_step}}}
The flux estimates, $s_k$, for each star can be considered individually. At step $j$ we can refine a star's flux estimate (to $s_{kj+1}$) by minimizing the error function with the latest flat-field parameters:

\begin{equation}
\chi^2_{k} = \sum_{i \in \mathcal{O}(k)} \frac{(c_i-f_{ij}s_{kj})^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\frac{d\chi^2_{k}}{d s_{kj}} = \sum_{i \in \mathcal{O}(k)} \frac{-2 f_{ij} (c_i-f_{ij}s_{kj+1})}{{\sigma_i}^2} = 0
\end{equation}

\begin{equation}
\Rightarrow \sum_{i \in \mathcal{O}(k)} \frac{f_{ij} c_i}{{\sigma_i}^2}= \sum_{i \in \mathcal{O}(k)} \frac{f_{ij}^2 s_{kj+1}}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\Rightarrow s_{kj+1} = {\sum_{i \in \mathcal{O}(k)} \frac{f_{ij} c_i}{{\sigma_i}^2}}/{\sum_{i \in \mathcal{O}(k)} \frac{f_{ij}^2}{{\sigma_i}^2}}
\end{equation}

\subsection{Flat-Field Refinement: \textbf{\textit{p\_step}}}
The flat-field parameters can now be refined with the latest star flux estimates. Minimise error function with respect to the...

Consider all measurements

\begin{equation}
\chi^2 = \sum_{all~i} \frac{(c_i-f_{ij}s_{kj})^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
f_{ij} = \sum_{l = 1}^L q_{lj} g_i(\vec{x_i})
\end{equation}

\begin{equation}
\chi^2 = \sum_{all~i} \frac{(c_i- s_{kj} \sum_{l = 1}^L q_{lj} g_i(\vec{x_i}))^2}{{\sigma_i}^2}
\end{equation}

\begin{equation}
\frac{d\chi^2}{dq_{lj}} = \sum_{all~i} \frac{-2 g_l(\vec{x_i}) s_{kj+1} (c_i- s_{kj} \sum_{l = 1}^L q_{lj} g_i(\vec{x_i}))}{{\sigma_i}^2} = 0
\end{equation}

\begin{equation}
\sum_{all~i} \frac{g_l(\vec{x_i}) s_{kj+1} c_i}{{\sigma_i}^2} = \sum_{all~i} \frac{g_l(\vec{x_i}) s_{kj+1}^2 \sum_{l = 1}^L q_{lj+1} g_l(\vec{x_i})}{{\sigma_i}^2}
\end{equation}
